---
title: "Untitled"
output: html_document
date: "2024-11-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Packages
```{r}
library(tidyverse)
library(stringr)
library(rvest)
library(hoopR)
```

KenPom FanMatch Python Data Load & Manipulation (kenpompy)
```{r}
# Get today's date in "yyyymmdd" format
current_date <- format(Sys.Date(), "%Y%m%d")

# Construct the filename and read the CSV file
file_name <- paste0("fanmatch_", current_date, ".csv")
df_name <- paste0("fanmatch_", current_date)

# Read the CSV, select specific columns, and filter out rows with NA in 'PredictedWinner'
temp_df <- read_csv(file_name) %>% 
  select(1, 3, 10, 11, 14) %>% 
  filter(!is.na(PredictedWinner)) %>%
  mutate(
    # Replace occurrences of two spaces after "at" or "vs" with a single space
    Game = str_replace_all(Game, "(?<=\\s(at|vs))\\s{2,}", " "),
    
    # Extract the home ranking number (first part before the first space)
    away_rk = as.numeric(str_extract(Game, "^\\d+")),
    
    # Extract the home team name (from after the home ranking to the first " at " or " vs ")
    away = str_extract(Game, "(?<=\\d\\s)([A-Za-z&\\s\\.]+)(?=\\s(?:at|vs)\\s)"),
    
    # Extract the away ranking number (the part after " at " or " vs " and before the second space)
    home_rk = as.numeric(str_extract(Game, "(?<=\\s(?:at|vs)\\s)\\d+")),
    
    # Extract the away team name (after the second ranking number)
    home = sub(".*(at|vs)[[:space:]]*\\d+[[:space:]]*(.*)", "\\2", Game),
    
    # Determine if the game is at a neutral site (1 for "vs", 0 for "at")
    neutral = if_else(str_detect(Game, "\\svs\\s"), 1, 0)
  ) 

temp_df <- temp_df %>%
  mutate(
    # Extract the scores using regex
    home_score = sapply(1:nrow(temp_df), function(i) {
      scores <- regmatches(temp_df$PredictedWinner[i], regexpr("\\d{2,3}-\\d{2,3}", temp_df$PredictedWinner[i]))
      score_win <- as.numeric(strsplit(scores, "-")[[1]][1])
      score_lose <- as.numeric(strsplit(scores, "-")[[1]][2])
      
      # Assign home score based on team name
      if(grepl(temp_df$home[i], temp_df$PredictedWinner[i])) {
        return(score_win)
      } else {
        return(score_lose)
      }
    }),
    
    away_score = sapply(1:nrow(temp_df), function(i) {
      scores <- regmatches(temp_df$PredictedWinner[i], regexpr("\\d{2,3}-\\d{2,3}", temp_df$PredictedWinner[i]))
      score_win <- as.numeric(strsplit(scores, "-")[[1]][1])
      score_lose <- as.numeric(strsplit(scores, "-")[[1]][2])
      
      # Assign away score based on team name
      if(grepl(temp_df$away[i], temp_df$PredictedWinner[i])) {
        return(score_win)
      } else {
        return(score_lose)
      }
    })
  ) %>%
  mutate(
    PredictedScore = as.numeric(gsub("[()%]", "", PredictedScore)) / 100,
    home_win_prob = ifelse(home_score > away_score, 
                           PredictedScore, 
                           1 - PredictedScore),
    away_win_prob = 1 - home_win_prob,
    home_spread = away_score - home_score,
    away_spread = home_score - away_score,
    total = home_score + away_score
  ) %>%
  mutate(
    Game = gsub("\\d+", "", Game),
    Game = str_replace_all(Game, "(?<=\\s(at|vs))\\s{2,}", " "),
    Game = str_trim(Game)
  ) %>% 
  select(1, 10, 2, 8, 9, 11, 6, 7, 12, 13:17)

# Assign the processed dataframe to a dynamically named variable
assign(df_name, temp_df)

# Clean up the temporary dataframe if needed
rm(temp_df)
```

#HoopR KenPom Data Load
```{r}
Sys.setenv(KP_USER = "nickaluk1030@gmail.com")
Sys.setenv(KP_PW = "N1ch0las103001")
login(user_email = Sys.getenv("KP_USER"), user_pw = Sys.getenv("KP_PW"))
temp_df <- kp_fanmatch(date = "2025-02-11")
temp_df <- temp_df %>%
  mutate()
```

KenPom FanMatch Excel Data Load & Manipulation
```{r}
setwd("~/Documents/SAL/KenPom Model/FanMatch csvs")
# Get today's date in "yyyymmdd" format
current_date <- format(Sys.Date(), "%Y%m%d")

# Construct the filename and read the CSV file
file_name <- paste0("fanmatchExcel_", current_date, ".csv")
df_name <- paste0("fanmatchExcel_", current_date)

#file_name <- paste0("fanmatchExcel_20241231.csv")
#df_name <- paste0("fanmatchExcel_20241231")

# Extracting the information in the "Game" column to new columns
#setwd("~/Documents/SAL/KenPom Model/FanMatch csvs")
temp_df <- read_csv(file_name) %>%
  slice(-1) %>% 
  select(1, 2, 5) %>%
  mutate(
    # Extract the away ranking number (first part before the first space)
    away_rk = as.numeric(str_extract(Game, "^\\d+")),
    
    # Extract the away team name (from after the away ranking to the first "at" or "vs.")
    away = str_extract(Game, "(?<=\\d\\s)([A-Za-z0-9&\\s\\.\\']+)(?=\\s(?:vs\\.|at)\\s)"),
    
    # Extract the home ranking number (the part after "at" or "vs." and before the second space)
    home_rk = as.numeric(str_extract(Game, "(?<=\\b(?:vs\\.|at)\\s)\\d+")),
    
    # Extract the home team name (after the home ranking number)
    home = str_extract(Game, "(?<=\\b(?:vs\\.|at)\\s)([A-Za-z0-9&\\s\\.\\']+)"),
    home = str_extract(home, "(?<=^\\d{1,3}\\s).*"),
    
    # Determine if the game is at a neutral site (1 for "vs., 0 for "at")
    neutral = if_else(str_detect(Game, "\\svs.\\s"), 1, 0)
  ) 

# Splitting of the "Prediction" column into two columns, "PredictedWinner" and "PredictedScore"
temp_df <- temp_df %>%
  rename(PredictedWinner = Prediction) %>% #Contains the winning team and score
  mutate(PredictedScore = str_extract(PredictedWinner, "\\(.*"),
         PredictedWinner = str_replace(PredictedWinner, "\\(.*", ""),
         PredictedWinner = str_trim(PredictedWinner),
         PredictedScore = str_sub(PredictedScore, 1, nchar(PredictedScore) - 5))
         # Contains the winning team's win percentage (%)

# List of words to remove
words_to_remove <- c("SEC", "B10", "B12", "BE", "ACC",
                     "MWC", "WCC", "A10", "Amer", "CUSA",
                     "MVC", "Ivy", "BW", "WAC", "SC",
                     "BSth", "CAA", "SB", "Horz", "Sum",
                     "BSky", "MAC", "Slnd", "ASun", "AE",
                     "MAAC", "PL", "OVC", "MEAC", "NEC", "SWAC")

# Modify the 'home' column
temp_df <- temp_df %>%
  mutate(home = if_else(str_extract(home, "\\S+$") %in% words_to_remove,
                        str_remove(home, "\\s\\S+$"),
                        home))

temp_df <- temp_df %>%
  mutate(
    # Extract the home and away scores using regex
    home_score = sapply(1:nrow(temp_df), function(i) {
      scores <- regmatches(temp_df$PredictedWinner[i], regexpr("\\d{2,3}-\\d{2,3}", temp_df$PredictedWinner[i]))
      score_win <- as.numeric(strsplit(scores, "-")[[1]][1])
      score_lose <- as.numeric(strsplit(scores, "-")[[1]][2])
      team_win <- sub("\\s\\d{2}-\\d{2}$", "", temp_df$PredictedWinner[i])
      
      # Assign home score based on team name within "home" and "PredictedWinner"
      if(temp_df$home[i] == team_win) {
        return(score_win)
      } else {
        return(score_lose)
      }
    }),
    away_score = sapply(1:nrow(temp_df), function(i) {
      scores <- regmatches(temp_df$PredictedWinner[i], regexpr("\\d{2,3}-\\d{2,3}", temp_df$PredictedWinner[i]))
      score_win <- as.numeric(strsplit(scores, "-")[[1]][1])
      score_lose <- as.numeric(strsplit(scores, "-")[[1]][2])
      team_win <- sub("\\s\\d{2}-\\d{2}$", "", temp_df$PredictedWinner[i])
      
      # Assign away score based on team name within "away" and "PredictedWinner"
      if(temp_df$away[i] == team_win) {
        return(score_win)
      } else {
        return(score_lose)
      }
    })
  ) %>%
  mutate(# Changing the "PredictedScore" column to a probability not percentage
    PredictedScore = as.numeric(gsub("[()%]", "", PredictedScore)) / 100,
    home_win_prob = ifelse(home_score > away_score, 
                           PredictedScore, 
                           1 - PredictedScore),
    away_win_prob = 1 - home_win_prob,
    ##### home_score = ifelse(home == "Iowa St.", 100, home_score),
    home_spread = away_score - home_score, # Calculating predicted spread from home and away scores
    away_spread = home_score - away_score,
    total = home_score + away_score # Calculating predicted total from home and away scores
  ) %>% 
  select(1, 2, 3, 8, 6, 7, 10, 4, 5, 11, 12:16)

# Duplication of rows where game is neutral site so multiple ids can be made for evantually merging with DraftKings data
temp_df <- temp_df %>%
  # Swapping of all home and away information
  bind_rows(
    temp_df %>%
      filter(neutral == 1) %>%
      mutate(
        home_rk_tmp = away_rk,
        away_rk = home_rk,
        home_tmp = away,
        away = home,
        home_score_tmp = away_score,
        away_score = home_score,
        home_win_prob_tmp = away_win_prob,
        away_win_prob = home_win_prob,
        home_spread_tmp = away_spread,
        away_spread = home_spread,
      ) %>%
      select(-home_rk, -home, -home_score, -home_win_prob, -home_spread) %>%
      rename(home_rk = home_rk_tmp,
             home = home_tmp,
             home_score = home_score_tmp,
             home_win_prob = home_win_prob_tmp,
             home_spread = home_spread_tmp,)
  )



# Creation of game ids through concatenating team names
temp_df <- temp_df %>%
  mutate(id = str_c(home, away, sep = "_"))

# Assign the processed dataframe to a dynamically named variable
assign(df_name, temp_df)

# Remove the temporary dataframe
rm(temp_df)
```

Draft Kings Lines Scrape
```{r}
# Define the URL
url <- "https://sportsbook.draftkings.com/leagues/basketball/ncaab?category=game-lines&subcategory=game"

# Read the HTML content from the webpage
webpage <- read_html(url)

# Scrape the text inside the <div class="event-cell__name-text">
team_names <- webpage %>%
  html_nodes(".event-cell__name-text") %>%
  html_text()

####### team_names <- team_names[!team_names %in% c("VMI", "Samford")]

away_teams <- team_names[seq(1, length(team_names), by = 2)]  # Odd-indexed values (away)
home_teams <- team_names[seq(2, length(team_names), by = 2)]  # Even-indexed values (home)

# Scraping the spread and total information from the text inside the <div class="sportsbook-outcome-cell">
lines <- webpage %>%
  html_nodes(".sportsbook-outcome-cell__line") %>%
  html_text()

####### lines <- lines[-c(93:95)]

# Defining indices to remove to remove duplicate spread and total information
indices_to_remove <- c(seq(3, length(lines), by = 4), seq(4, length(lines), by = 4))

# Remove the elements at these indices using negative indexing
lines <- lines[-indices_to_remove]

away_spread2 <- lines[seq(1, length(lines), by = 2)] # Odd-indexed values (away spread)
total2 <- lines[seq(2, length(lines), by = 2)] # Even-indexed values (total)
total2 <- as.numeric(total2)

# Creation of the dynamic dataframe name
df_name <- paste0("dk_", current_date)

# Create the temporary dataframe and assign it dynamically
temp_df <- data.frame(home = home_teams, away = away_teams, away_spread2 = away_spread2, total2 = total2)

# Remove the + sign from underdog spreads and change the column to numeric
temp_df$away_spread2 <- as.numeric(gsub("\\+", "", temp_df$away_spread2))

# Creation of home spread value
temp_df <- temp_df %>% 
  mutate(home_spread2 = away_spread2*-1) %>%
  select(1, 2, 5, 3, 4)
```

Remove Live/Future Days Games available for Betting
```{r}
# Removal of rows from the dataframe that contain games from future dates
# Will have to check https://sportsbook.draftkings.com/leagues/basketball/ncaab?category=game-lines&subcategory=game
temp_df <- temp_df[-c(141,142), ]
temp_df[1, c("home_spread2", "away_spread2", "total2")] <- c(7.5, -7.5, 149.5)
temp_df[2, c("home_spread2", "away_spread2", "total2")] <- c(-2.5, 2.5, 151.5)
temp_df[3, c("home_spread2", "away_spread2", "total2")] <- c(4.5, -4.5, 162.5)
```

Check team name differences
```{r}
# Change all "State" occurences in team names to "St." (what KenPom uses)
temp_df$home <- gsub("State", "St.", temp_df$home)
temp_df$away <- gsub("State", "St.", temp_df$away)
dknames <- c(temp_df$home, temp_df$away)

kenpomnames <- read_csv("kenpomnames.csv")

#Finding team names from DraftKings that are spelled/formatted differently on KenPom
teams_not_in_kenpom <- setdiff(dknames, kenpomnames$Team)
teams_not_in_kenpom
```

Update and check of known team name differences
```{r}
# Define the mapping vector for team name changes
team_name_changes <- c(
"NC Central" = "North Carolina Central",
"Ole Miss" = "Mississippi",
"ETSU" = "East Tennessee St.",
"Queens NC" = "Queens",
"Saint Josephs" = "Saint Joseph's",
"NC St." = "N.C. State",
"Nicholls St." = "Nicholls",
"Gardner-Webb" = "Gardner Webb",
"IU Indianapolis" = "IU Indy",
"UMass" = "Massachusetts",
"Grambling" = "Grambling St.",
"Saint Thomas MN" = "St. Thomas",
"Central Connecticut St." = "Central Connecticut",
"Saint Francis PA" = "Saint Francis",
"ULM" = "Louisiana Monroe",
"Texas A&M-Commerce" = "Texas A&M Commerce",
"Mount Saint Marys" = "Mount St. Mary's",
"SIU Edwardsville" = "SIUE",
"A&M-Corpus Christi" = "Texas A&M Corpus Chris",
"Saint Marys" = "Saint Mary's",
"California Baptist" = "Cal Baptist",
"Omaha" = "Nebraska Omaha",
"MD Eastern Shore" = "Maryland Eastern Shore",
"Prairie View" = "Prairie View A&M",
"Mississippi Valley" = "Mississippi Valley St.",
"CSU Bakersfield" = "Cal St. Bakersfield",
"Saint Bonaventure" = "St. Bonaventure",
"Saint Johns" = "St. John's",
"Albany NY" = "Albany",
"Alcorn" = "Alcorn St.",
"Arkansas-Pine Bluff" = "Arkansas Pine Bluff",
"UConn" = "Connecticut",
"Loyola Maryland" = "Loyola MD",
"SE Louisiana" = "Southeastern Louisiana",
"Bethune-Cookman" = "Bethune Cookman",
"Sam Houston" = "Sam Houston St.",
"UT Martin" = "Tennessee Martin",
"Pennsylvania" = "Penn",
"SE Missouri St." = "Southeast Missouri",
"UMKC" = "Kansas City",
"Southern University" = "Southern"
#East Texas A&M will pop up if they play but is changed within KenPom
)

# Identify teams in teams_not_in_kenpom that aren't in team_name_changes
teams_missing_in_changes <- teams_not_in_kenpom[!teams_not_in_kenpom %in% names(team_name_changes)]

# Print missing teams
teams_missing_in_changes
```

```{r}
# Replace values in 'home' column based on the mapping
temp_df$home <- sapply(temp_df$home, function(x) {
  if (x %in% names(team_name_changes)) {
    return(team_name_changes[x])
  } else {
    return(x)
  }
})

# Replace values in 'away' column based on the mapping
temp_df$away <- sapply(temp_df$away, function(x) {
  if (x %in% names(team_name_changes)) {
    return(team_name_changes[x])
  } else {
    return(x)
  }
})

# Again checking for differences in naming (should be = character(0))
dknames <- c(temp_df$home, temp_df$away)

teams_not_in_kenpom <- setdiff(dknames, kenpomnames$Team)
teams_not_in_kenpom
```

Dataframe renaming for automation
```{r}
temp_df <- temp_df %>%
  mutate(id = str_c(home, away, sep = "_"))
# Assign the processed dataframe to a dynamically named variable
#setwd("~/Documents/SAL/KenPom Model")
#temp_df <- read_csv("dk_20241231.csv")
#df_name <- paste0("dk_20241231")
assign(df_name, temp_df)

# Removing the temporary dataframe
rm(temp_df)
```

Value Picks (> 3 for Spread, > 5 for Total)
```{r}
# Creation of dynamic names for the two dataframes for merging
dk_name <- paste0("dk_", current_date)
fanmatch_name <- paste0("fanmatchExcel_", current_date)

#dk_name <- paste0("dk_20241231")
#fanmatch_name <- paste0("fanmatchExcel_20241231")

# Joining of the DraftKings relevant columns with the KenPom data on "id"
df_joined <- get(dk_name) %>%
  select(id, home_spread2, away_spread2, total2) %>%
  left_join(get(fanmatch_name), by = "id") %>%
  select(5:19, 2:4) %>%
  mutate(away_value = away_spread2 - away_spread, # Value columns created
         home_value = home_spread2 - home_spread,
         over_value = total - total2,
         under_value = total2 - total)

# Finding away teams with value spreads
away_picks <- df_joined %>%
  filter(away_value > 3) %>%
  mutate(picks = if_else(away_spread2 > 0,
                              paste(away, "+", away_spread2),
                              paste(away, "", away_spread2))) %>%
  select(picks, Game, PredictedWinner, neutral, away_spread, away_spread2, away_value) %>%
  rename(spread = away_spread,
         spread2 = away_spread2,
         value = away_value)

# Finding home teams with value spreads
home_picks <- df_joined %>%
  filter(home_value > 3) %>%
  mutate(picks = if_else(home_spread2 > 0,
                              paste(home, "+", home_spread2),
                              paste(home, "", home_spread2))) %>%
  select(picks, Game, PredictedWinner, neutral, home_spread, home_spread2, home_value) %>%
  rename(spread = home_spread,
         spread2 = home_spread2,
         value = home_value)

# Binding of the away and home spread picks
spread_picks <- bind_rows(away_picks, home_picks)

# Finding value picks for the over
over_picks <- df_joined %>%
  filter(over_value > 5) %>%
  mutate(picks = paste0("o", total2)) %>%
  select(picks, Game, PredictedWinner, neutral, total, total2, over_value) %>%
  rename(value = over_value)

# Finding value picks for the under
under_picks <- df_joined %>%
  filter(under_value > 5) %>%
  mutate(picks = paste0("u", total2)) %>%
  select(picks, Game, PredictedWinner, neutral, total, total2, under_value) %>%
  rename(value = under_value)

# Binding of the over and under total picks
total_picks <- bind_rows(over_picks, under_picks)

# View the picks dataframes
print(spread_picks)
print(total_picks)
```


